Exact Asymptotics for Causal Mediation Analysis

### 2024-05-30 notes/William Analysis.Rmd
Run analysis for binary-binary-mixed case

# Fewer large sample sizes
# all_Ns = c(100, 200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000, 2000)
all_Ns = c(200, 500, 1000)

@@

# Number of clusters
K=5

@@

@@

  for(i in 1:num_reps){
    print(paste0("n = ", n, ", i = ", i, " of ", num_reps))

@@

# Save output
# save(all_a_hats, all_theta_hats, all_b_hats, all_gamma_hats, all_M_covs, all_Y_covs, all_med_hats, all_med_SEs, file = "William-Analysis_cache/MC-bin-bin-mix.RData")
# load("William-Analysis_cache/MC-bin-bin-mix.RData")
```

@@

# Combine into a table
# results = data.frame(Empirical = emp_SEs,
#                      Mean = mean_delta_SEs, Median = median_delta_SEs,
#                      "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
#                      "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)
results = data.frame(n = all_Ns, Empirical = emp_SEs,
                     Mean = mean_delta_SEs, Median = median_delta_SEs,
                     "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
                     "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)

@@

med_hats_to_plot = unlist(data_med_hats)
Ns_to_plot = rep(all_Ns, times = sapply(data_med_hats, length))
data_med_hat_to_plot = data.frame(med_hat = med_hats_to_plot, N = Ns_to_plot)

@@

ggplot(data_med_hat_to_plot, aes(x = med_hat)) +
  # geom_histogram(bins = 30) +
  geom_density() +
  facet_wrap(~N, scales = "free") +
  theme_minimal()

# QQ plot for each sample size
ggplot(data_med_hat_to_plot, aes(sample = med_hat)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~N, scales = "free") +
  theme_minimal()

# Test normality in each sample size
all_norm_p_vals = c()
for(n in all_Ns){
  p_val = shapiro.test(data_med_hat_to_plot$med_hat[data_med_hat_to_plot$N == n])$p.value
  all_norm_p_vals = c(all_norm_p_vals, p_val)
}
all_norm_p_vals
```

>>>>

# Fewer large sample sizes
# all_Ns = c(100, 200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000)
all_Ns = c(200, 500, 1000)

@@

# Number of clusters
all_Ks = c(5, 20, 50)
# K=5

N_K_combs = expand.grid(N = all_Ns, K = all_Ks)

@@

for(j in seq_len(nrow(N_K_combs))){
  n = N_K_combs[j, "N"]
  K = N_K_combs[j, "K"]

@@

  for(i in 1:num_reps){
    print(paste0("n = ", n, ", K = ", K, ", i = ", i, " of ", num_reps))

@@

# Save output
# save(all_a_hats, all_theta_hats, all_b_hats, all_gamma_hats, all_M_covs, all_Y_covs, all_med_hats, all_med_SEs, file = "William-Analysis_cache/MC-bin-bin-mix-n=200,500,1000.RData")
# load("William-Analysis_cache/MC-bin-bin-mix.RData")
```

@@

# Combine into a table
# results = data.frame(Empirical = emp_SEs,
#                      Mean = mean_delta_SEs, Median = median_delta_SEs,
#                      "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
#                      "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)
# results = data.frame(n = all_Ns, Empirical = emp_SEs,
#                      Mean = mean_delta_SEs, Median = median_delta_SEs,
#                      "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
#                      "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)
results = data.frame(n = N_K_combs$N, K = N_K_combs$K, Empirical = emp_SEs,
                     Mean = mean_delta_SEs, Median = median_delta_SEs,
                     "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
                     "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)

@@

med_hats_to_plot = unlist(data_med_hats)
Ns_to_plot = rep(N_K_combs$N, times = sapply(data_med_hats, length))
Ks_to_plot = rep(N_K_combs$K, times = sapply(data_med_hats, length))
data_med_hat_to_plot = data.frame(med_hat = med_hats_to_plot, N = Ns_to_plot, K = Ks_to_plot)

@@

ggplot(data_med_hat_to_plot, aes(x = med_hat)) +
  # geom_histogram(bins = 30) +
  geom_density() +   theme_minimal() +
  facet_grid(rows = vars(N), cols = vars(K), scales = "free")

# QQ plot for each sample size
ggplot(data_med_hat_to_plot, aes(sample = med_hat)) +
  stat_qq() +
  stat_qq_line() +
  facet_grid(rows = vars(N), cols = vars(K), scales = "free")
  theme_minimal()

# Test normality in each sample size
all_norm_p_vals = c()
for(i in 1:nrow(N_K_combs)){
  p_val = shapiro.test(data_med_hats[[i]])$p.value
  all_norm_p_vals = c(all_norm_p_vals, p_val)
}

results$Shapiro_p = all_norm_p_vals
results
```
